Combining living and fossil taxa into phylogenies: the missing data issue

### 2015-07-29 Manuscript/MPESubmission/Revision/response.tex

We added the following sentence to the main text to clarify and link to the supplementary analysis:
"In practice, the difference between the ``true'' and the ``best'' tree represents the effect of our parameters and R packages choices (i.e. diversitree, phyclust and ape) as well as the phylogenetic methods used (see appendix B).
The aim of this study, however, is to look at the effect the missing data parameters described above on topological recovery." (line @@@).

% TG: not sure how this justifications sounds...

### 2015-07-29 Manuscript/MPESubmission/Revision/TEM_revised_manuscript.tex
Starting tree effect (tmp - missing tables)

\subsection{Estimating phylogenies}
From the resulting matrices we generated two types of trees: the ``best'' tree inferred from the ``complete'' matrix and the ``missing-data'' trees inferred from the 125 matrices with various amounts of missing data.
The ``true'' tree was used to generate the ``complete'' matrix and reflects the ``true'' evolutionary history in our simulations.
The ``best'' tree, on the other hand, is the best tree we can build using state-of-the-art phylogenetic methods.
In real world situations, the ``true'' tree is never available to us because we cannot know the true evolutionary history of a clade \citep[except in very rare circumstances, e.g.][]{rozen2005}.
Therefore, here we focus on comparing the trees inferred from the matrices with missing data to the ``best'' tree, rather than the ``true'' tree, as the ``best'' tree is generally what we have to work with.

>>>>

\subsection{Estimating phylogenies}
From the resulting matrices we generated two types of trees: the ``best'' tree inferred from the ``complete'' matrix and the ``missing-data'' trees inferred from the 125 matrices with various amounts of missing data.
The ``true'' tree was used to generate the ``complete'' matrix and reflects the ``true'' evolutionary history in our simulations.
The ``best'' tree, on the other hand, is the best tree we can build using state-of-the-art phylogenetic methods.
In real world situations, the ``true'' tree is never available to us because we cannot know the true evolutionary history of a clade \citep[except in very rare circumstances, e.g.][]{rozen2005}.
\hl{In practice, the difference between the ``true'' and the ``best'' tree represents the effect of our parameters and R packages choices (i.e. diversitree, phyclust and ape) as well as the phylogenetic methods used (see appendix B).}
\hl{The aim of this study, however, is to look at the effect the missing data parameters described above on topological recovery.}
Therefore, here we focus on comparing the trees inferred from the matrices with missing data to the ``best'' tree, rather than the ``true'' tree, as the ``best'' tree is generally what we have to work with.
